Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-08 paper/paper.Rmd

```{r}
BayesFactor::meta.ttestBF(d$origin_t_stat, d$original_t_df)
BayesFactor::meta.ttestBF(d$rep_t_stat, d$rep_t_df)
```
@etz2016

>>>>

```{r}
getBF <- function(t_stat, t_df) {
  return(ttest.tstat(t = t_stat, n1 = t_df, rscale = 1, simple = T))
};

tstatDF <- d %>%
  filter(original_t_stat != "NA") %>%
  select(project_key, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
  rowwise() %>%
  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
  rowwise() %>%
  mutate(repBF = getBF(rep_t_stat, rep_t_df))

ggplot(tstatDF, aes(x = origBF, y = repBF, size = rep_t_df/original_t_df)) +
  geom_point()+
  theme_bw()+
  # xlim(-2, 30) +
  # ylim(-2, 30) +
  geom_hline(aes(yintercept = 10), linetype = 2)+
  geom_hline(aes(yintercept = 3), linetype = 2)+
  geom_hline(aes(yintercept = 1/3), linetype = 2)+
  geom_hline(aes(yintercept = 1/10), linetype = 2)+
  geom_vline(aes(xintercept = 10), linetype = 2)+
  geom_vline(aes(xintercept = 3), linetype = 2)+
  geom_vline(aes(xintercept = 1/3), linetype = 2)+
  geom_vline(aes(xintercept = 1/10), linetype = 2) +
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1/3, 3, 10),
                labels = c("1/10", "1/3", "3", "10")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1/3, 3, 10),
                labels = c("1/10", "1/3", "3", "10"))

```
@etz2016
